Analysis of regime difference test results

### 2024-11-01 others/regime difference test results analysis.qmd

summary_individuals <- group_by(individuals, country, period, moment) %>%
  summarise(
    `10%` = sum(`p-value` > 0.05 & `p-value` <= 0.1, na.rm = TRUE),
    `5%` = sum(`p-value` > 0.01 & `p-value` <= 0.05, na.rm = TRUE),
    `1%` = sum(`p-value` > 0 & `p-value` <= 0.01, na.rm = TRUE),
    .groups = "drop"
  )

@@

summary_individuals <- group_by(individuals, country, period, moment) %>%
  summarise(
    `10%` = list(name[`p-value` >= 0.05 & `p-value` < 0.1]),
    `5%` = list(name[`p-value` >= 0.01 & `p-value` < 0.05]),
    `1%` = list(name[`p-value` >= 0 & `p-value` < 0.01]),
    .groups = "drop"
  )

@@

significance <- function(x) {
  case_when(
    x > 0.1 ~ "",
    x > 0.05 ~ "*",
    x > 0.01 ~ "**",
    TRUE ~ "***"
  )
}

>>>>

summary_individuals <- dplyr::group_by(individuals, country, period, moment) %>%
 dplyr::summarise(
    `10%` = sum(`p-value` > 0.05 & `p-value` <= 0.1, na.rm = TRUE),
    `5%` = sum(`p-value` > 0.01 & `p-value` <= 0.05, na.rm = TRUE),
    `1%` = sum(`p-value` > 0 & `p-value` <= 0.01, na.rm = TRUE),
    .groups = "drop"
  )

@@

summary_individuals <- dplyr::group_by(individuals, country, period, moment) %>%
  dplyr::summarise(
    `10%` = list(name[`p-value` >= 0.05 & `p-value` < 0.1]),
    `5%` = list(name[`p-value` >= 0.01 & `p-value` < 0.05]),
    `1%` = list(name[`p-value` >= 0 & `p-value` < 0.01]),
    .groups = "drop"
  )

@@

significance <- function(x) {
  dplyr::case_when(x > 0.1 ~ "", x > 0.05 ~ "*", x > 0.01 ~ "**", TRUE ~ "***")
}
